Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-12-04 ms.qmd
Newline

#### Affliations:
$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia <br />
$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia <br />
$^3$ SOLES, University of Sydney, Sydney, NSW, Australia <br />
$^4$ Department of Biology, Lancaster University, Liverpool, UK

>>>>

#### Affliations:
$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;  
$^3$ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
$^4$ Department of Biology, Lancaster University, Liverpool, UK
